% $\ihalf$ = 1/2
% $\iiiquarter$ = 3/4
% $\iithirds$ = 2/3
% $\ithird$ = 1/3
% $\iquarter$ = 1/4
% $\ieight$ = 1/8

\recipe{
%Title
Chicken Pie in a Mug
}[
%Optional initial instructions. \temp{350} for temperature.
]

\begin{step}
%. . Notes
%Ingredients for this step
3-4 tablespoons cooked chicken
2 tablespoons frozen vegetables (peas and carrots)
1$\ihalf$ teaspoons cornstarch
To taste Salt and pepper
\method
In a large microwavable mug add in the cooked chicken, frozen vegetables, cornstarch, salt and pepper. Stir well together to mix in the cornstarch.
%Step1
\end{step}

\begin{step}
%Ingredients for this step
3 tablespoons chicken stock
1 tablespoon milk
\method
Pour in the stock and milk and stir well until everything is combined. Set aside.
%Step2
\end{step}

\begin{step}
%. . Notes
%Ingredients for this step
4 tablespoons flour
$\ihalf$ teaspoon baking powder
$\ieight$ teaspoon salt
\method
For the biscuit topping: Mix together the flour, baking powder and salt in a small bowl.
%Step3
\end{step}

\begin{step}
%Ingredients for this step
$\ihalf$ tablespoon butter, cubed
\method
Using a fork rub in the cubed butter into the dry ingredients.
%Step2
\end{step}

\begin{step}
%Ingredients for this step
3$\ihalf$ tablespoons milk
1 tablespoon chopped herbs
\method
Stir in the milk and herbs until your mix forms a batter.

Gently scoop the batter on top of the chicken pie mix. It might sink a little, don’t worry that is fine. During cooking it will rise up.

Microwave (1200W) for roughly 2 minutes- 2 minutes 15 seconds. It is ready when the biscuit batter is firm on top and you don’t see any wet batter.
%Step2
\end{step}